---
title: "Presentation from Rmd file. The name is loooong"
author: "Vadim K."
date: "16 March 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## New slide
Some content

- Bullet one
- Bullet two

1. Item a
2. Item b

***
Slide without heading

###Only with

####Subheadings


##Slide with some code
```{r, comment="", echo=TRUE}
head(mtcars)
```

```{r, comment="", echo=TRUE, eval=FALSE}
#not evaluated
plot(mtcars)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

